Offshore Blue Crab Densities for <br/> The Gulf of Mexico

### 2020-01-29 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
end of offshore model

## Candidate Models

**Model Selection using AIC**

@@

**Predictor Significance using Chi-Square LRT and Deviance**

@@

@@

@@

# #Observed data
# mean_obs <- mean(seamap_west$cpue_towspd)
# obs_timeline <- seamap_west %>% 
#   group_by(survey_year, region, season) %>% 
#   summarise(Nobs = n(),
#             PercentPos = mean(crab_presence),
#             Mean_CPUE = mean(cpue_towspd)) %>% 
#   mutate(Index_Obs = Mean_CPUE/mean_obs)

#ggplot of standardized index of abundance
p <- best_mod_dat %>% 
  mutate(year_n = as.numeric(as.character(year_f))) %>% 
  ggplot(aes(year_n, response)) +
      #Fitted Data
      geom_line(aes(year_n, response, color = season)) +
      geom_point(aes(year_n, response, color = season, shape = season)) +
      # Observed Data
      # geom_line(data = obs_timeline, 
      #         aes(survey_year, Mean_CPUE, group = region), 
      #         col = "royalblue", linetype = 2) +
      # geom_point(data = obs_timeline, 
      #            aes(survey_year, Mean_CPUE, group = region), col = "royalblue") +
      scale_color_grey(start = 0.2, end = 0.6) + 
      labs(
        x = NULL, 
        y = "Crabs per Hectare",
        title = "Model Estimates and Yearly observed means") +
      facet_grid(region ~ .) +
  theme(
    legend.position = c(1, .98),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    legend.title = element_blank())
p

>>>>

## Candidate Models {.tabset}

### Model Selection using AIC

@@

### Predictor Significance

@@

bind_rows(
  list(
    lrt_y  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor"),
    lrt_r  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
    lrt_s  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor") %>% filter(Predictor == "season"),
    lrt_yr  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor") %>% filter(Predictor == "year_f:region")
)) %>% kable()

@@

Statistic reported below is the Wald Chi-Square z-score.

```{r}
#summary(best_mod) #to see what test statistic is used
broom::tidy(best_mod) %>% kable()
```

```{r}
emmip(best_mod, region ~ year_f, type = "response", offset = 0) + labs(x = NULL, caption = "Interaction Plot for year * region factors")
```

@@

# Catch Plot
p <- best_mod_dat %>% 
  mutate(year_n = as.numeric(as.character(year_f))) %>% 
  ggplot(aes(year_n, response)) +
      geom_line(aes(year_n, response, color = season)) +
      geom_point(aes(year_n, response, color = season, shape = season)) +
      scale_color_grey(start = 0.2, end = 0.6) + 
      labs(
        x = NULL, 
        y = "Crabs per Hectare",
        title = "Model Estimates and Yearly observed means") +
      facet_grid(region ~ .) +
  theme(
    legend.position = c(1, .98),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    legend.title = element_blank())
p
